On Secure Delegation of SampBQP with a Classical Client

### 2020-04-05 qpip.tex
Implement a couple more suggestions

We start with a $\SampBQP$ problem $(D_x)_{x\in\set{0, 1}^*}$ and an input $x$,
then there exists some quantum circuit $C$ that samples from $D_x$ within desired accuracy. \Ethan{Define some kinda $\varepsilon_0$ for this}
We assume without loss of generality that $C$ comprises of only Hadamard and Toffoli gates.
We present our protocol that allows a client to verifiably obtain the measurement outcome of $C(x)$.

\begin{protocol}{$\QPIP_1$ protocol $\PiSamp=(\PSamp, \VSamp)$ for the computation $C(x)$ with error parameter $\varepsilon$}
	\label{ProtoQPIP1}

	Inputs:
	\begin{itemize}
		\item Error parameter $\varepsilon\in(0, 1)$
		\item Input string $x\in\set{0, 1}^n$
		\item Quantum circuit $C$ of size $T$ consisting of only Hadamard and Toffoli gates \Ethan{move this into ingredients and put SampBQP instance as inputs}
	\end{itemize}

	Ingrediants:
	\begin{itemize}
		\item Let $C'$ be $C$ padded with $\frac{T}{\varepsilon}$ identity gates at the end.
		\item Let $\ket{\psi_{C'(x)}}$ be the local Hamiltonian ground state associated with $C'$ as defined in \Cref{thm:LHReduction}. \Ethan{Also bring $H_C$ in. More descriptions. Make it more intuitive.}
		\item $\cVGS$ be the way to check said ground state as defined in \Cref{AlgGroundStateCheck}. \Ethan{TODO wording needs fix}
		\item Define $c\in\bbR$ as in \Cref{cor:HamCheck}. \Ethan{Just make sure it's less than 10 and write 10. Also it shouldn't be an ingredient if it's $c$}
	\end{itemize}

	Protocol:
	\begin{enumerate}
		\item The honest prover prepares $M=\frac{T^{21}}{\varepsilon^{33}}$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{10}}{\varepsilon^{15}}$, and $k\xleftarrow{\$}[M]\setminus I$.
			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
		\begin{enumerate}
			\item If $i\in I$, run $z_i\leftarrow\cV_{\GS}(\rho_i)$.
			\item Else if $i=k$, measure the data register \Ethan{Revisit this name} of $\rho_i$ under the standard basis and save the outcome as $y$.
			\item Else, discard $\rho_i$.
		\end{enumerate}
			Let $Z=\sum_{i\in I} z_i$. If $Z>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{2\left(T+\frac{T}{\varepsilon}\right)^5}$ then the verifier accepts and outputs $y$. Otherwise, it rejects.
	\end{enumerate}
\end{protocol}

@@

	The soundness errors at each step is $O(\varepsilon)$, so the conclusion follows.
	\Ethan{Be more careful here. Actually sum up errors.}
\end{prf}

>>>>

\begin{protocol}{$\QPIP_1$ protocol $\PiSamp=(\PSamp, \VSamp)$ for $\SampBQP$}
	\label{ProtoQPIP1}

	Inputs:
	\begin{itemize}
		\item $\SampBQP$ instance $(D_x)_{x\in\set{0, 1}^*}$
		\item Classical input $x\in\zo^n$ to the $\SampBQP$ instance
		\item Error parameter $\varepsilon\in(0, 1)$
	\end{itemize}

	Ingrediants:
	\begin{itemize}
		\item Quantum circuit $C$ of size $T$ consisting of only Hadamard and Toffoli gates \Ethan{Something about $\varepsilon_0$?}
		\item Let $C'$ be $C$ padded with $\frac{T}{\varepsilon}$ identity gates at the end.
		\item Let $\ket{\psi_{C'(x)}}$ be the local Hamiltonian ground state associated with $C'$ as defined in \Cref{thm:LHReduction}. \Ethan{Also bring $H_C$ in. More descriptions. Make it more intuitive.}
		\item $\cVGS$ be the way to check said ground state as defined in \Cref{AlgGroundStateCheck}. \Ethan{TODO wording needs fix}
	\end{itemize}

	Protocol:
	\begin{enumerate}
		\item The honest prover prepares $M=\frac{T^{21}}{\varepsilon^{33}}$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{10}}{\varepsilon^{15}}$, and $k\xleftarrow{\$}[M]\setminus I$.
			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
		\begin{enumerate}
			\item If $i\in I$, run $z_i\leftarrow\cV_{\GS}(\rho_i)$.
			\item Else if $i=k$, measure the data register \Ethan{Revisit this name} of $\rho_i$ under the standard basis and save the outcome as $y$.
			\item Else, discard $\rho_i$.
		\end{enumerate}
			Let $Z=\sum_{i\in I} z_i$. If $Z>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{2\left(T+\frac{T}{\varepsilon}\right)^5}$ and $c\in\bbR$ as in \Cref{cor:HamCheck} then the verifier accepts and outputs $y$. Otherwise, it rejects.
	\end{enumerate}
\end{protocol}

@@

	The soundness errors at each step is $O(\varepsilon)$, so the conclusion follows.
	\Ethan{Be more careful here. Actually sum up errors.}
\end{prf}
\begin{cor}
	By choosing $\tilde{\varepsilon}=O(\varepsilon)$ accordingly, $\PiSamp$ has $\tilde\varepsilon$ soundness error. In which case, it runs in $\poly(T, \tilde\varepsilon^{-1})$ time, and has negligible completeness errors.
\end{cor}
